---
title: "linear model from Web"
author: "Daniel Esteves"
date: "summer 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

# Methods
all variables are numerical, so we use num~num for all 3 parts.


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### descriptive results -- scatterplot

```{r}
plot(SIMS~ARM,data=data)
```


The scatter plot shows that as ARM values increase, the SMS values also generally increase, suggesting a positive relationship between the two variables.  

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
A correlation coefficient of 0.6860073 means there's a strong positive relationship between ARM and SMS, so when one goes up, the other usually does too.

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
#### scatterplot with model fit
```{r}
plot(SIMS~ARM,data=data)
abline(model.1, col='blue')
```

The p-values for both the intercept and the slope are less than 2e-16, showing that there's a very strong and significant relationship between ARM and SMS.  

#### Predict at target point

```{r}
newdata = data.frame(ARM = 88, GRIP=94)
predict(model.1, newdata, interval='pred')
```
 The SIMS prediction for ARM=88 is 0.71, the predicting is (-1.73, 3.14)


## Model 2 SIM~GRIP

### Now add in scatterplot
```{r}
plot(SIMS~GRIP,data=data)
```

The scatter plot shows that as GRIP scores increase, SMS scores also generally go up, indicating a positive relationship between the two variables.  


### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

This shows that when GRIP strength increases the simulation will be positive.  

### Inferential  (Build model.2)
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```  

#### scatterplot with model fit
```{r}
plot(SIMS~GRIP,data=data)
abline(model.2, col='blue')
```

The p-values for both the intercept and slope are less than 2e-16, meaning they are both very significant and there's a strong link between GRIP and SMS.  
#### predict model.2 at target point

```{r}
newdata = data.frame(ARM =88, GRIP=94)
predict(model.2, newdata, interval='pred')
```

The SIMS prediction for GRIP=94 is -0.54, the predicting interval is (-3.11, 2.04)

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

